Spfy: an integrated graph database for real-time prediction of Escherichia coli phenotypes and downstream comparative analyses

### 2018-04-19 paper-webserver.tex
STOP: off to DG

\author[1]{Kevin K Le\thanks{kevin.le@canada.ca}}
\author[1]{Matthew D Whiteside}
\author[1]{James Hopkins}
\author[1]{Victor PJ Gannon}
\author[1]{Chad R Laing\thanks{chad.laing@canada.ca}}
\affil[1]{National Microbiology Laboratory at Lethbridge, Public Health Agency of Canada, Twp Rd 9-1, Lethbridge, AB, T1J 3Z4, Canada}

@@

% This is still true. The text needs to be larger: --> The text in this figure is too small to read and seems blurry. It should be enlarged.
\begin{figure}[!hb]
\begin{center}
\includegraphics[width=\textwidth]{images/ontology_r3}
\end{center}
\caption{Structure of the Spfy graph database. Brackets highlight the source of different data points and the software it was generated from. Data are added in as the analysis modules complete, at varying times, and the overall connections are inferred by the database. Non-bracketed sections are sourced from the uploaded genome files or user-supplied metadata.}
\label{fig-ontology}
\end{figure}

@@

% The X and Y axes labels need to be slightly larger. Designate the panes a), b), and c) and then reference them in the caption. The caption should contain the information that the titles on each pane currently do.
\begin{figure}[!htb]
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{images/fishers_genomes.png}
\endminipage\hfill
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{images/fishers_targets.png}
\endminipage\hfill
\minipage{0.32\textwidth}%
  \includegraphics[width=\linewidth]{images/fishers_overall.png}
\endminipage
\caption{Runtimes of Fisher's Exact Test depending on the number of nodes/attributes involved in the comparison. Left: Runtimes as the number of genomes increased for a fixed (107) number of targets per genome. Center: Runtimes as the number of targets increased for a fixed (116) number of genomes per target. Right: Runtimes as the total number of targets retrieved increased; the total number of targets was calculated as follows: (Number Genomes Group A + Number Genomes Group B) x Number Targets per Genome. In all cases, a linear increase in runtime was observered as the number of targets or genomes increased.}\label{fig:fishers_performance}
\end{figure}

@@

\begin{figure}[!htb]
\minipage{0.5\textwidth}%
  \includegraphics[width=\linewidth]{images/spfy_batches_totals.png}
\endminipage
\caption{Total runtimes of Spfy's analysis modules for batches of files. The blue line indicates the actual time to completion after accounting for parallelization; 50 files are analyzed in 45 minutes and 100 files in 89 minutes.}\label{fig:spfy_performance}
\end{figure}

>>>>

\author[1]{Kevin K Le\thanks{kevin.le@canada.ca}}
\author[1]{Matthew D Whiteside}
\author[1]{James E Hopkins}
\author[1]{Victor PJ Gannon}
\author[1]{Chad R Laing\thanks{chad.laing@canada.ca}}
\affil[1]{National Microbiology Laboratory at Lethbridge, Public Health Agency of Canada, Twp Rd 9-1, Lethbridge, AB, T1J 3Z4, Canada}

@@

\begin{figure}[!hb]
\begin{center}
\includegraphics[width=\textwidth]{images/ontology_r6}
\end{center}
\caption{Structure of the Spfy graph database. Brackets highlight the source of different data points and the software it was generated from. Data are added in as the analysis modules complete, at varying times, and the overall connections are inferred by the database. Non-bracketed sections are sourced from the uploaded genome files or user-supplied metadata. Figure was generated using \url{http://www.visualdataweb.de/webvowl/}.}
\label{fig-ontology}
\end{figure}

@@

% The X and Y axes labels need to be slightly larger. Designate the panes a), b), and c) and then reference them in the caption. The caption should contain the information that the titles on each pane currently do.
\begin{figure}[!htb]
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{images/fishers_genomes.png}
\endminipage\hfill
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{images/fishers_targets.png}
\endminipage\hfill
\minipage{0.32\textwidth}%
  \includegraphics[width=\linewidth]{images/fishers_overall.png}
\endminipage
\caption{Runtimes of Fisher's Exact Test depending on the number of nodes/attributes involved in the comparison. A: Runtimes as the number of genomes increased for a fixed (107) number of targets per genome. B: Runtimes as the number of targets increased for a fixed (116) number of genomes per target. C: Overall runtimes as the total number of targets retrieved increased; the total number of targets was calculated as follows: (Number Genomes Group A + Number Genomes Group B) x Number Targets per Genome. In all cases, a linear increase in runtime was observered as the number of targets or genomes increased.}\label{fig:fishers_performance}
\end{figure}

@@

\begin{figure}[!htb]
\begin{center}
\minipage{0.5\textwidth}%
  \includegraphics[width=\linewidth]{images/spfy_batches_totals.png}
\endminipage
\caption{Total runtimes of Spfy's analysis modules for batches of files. The blue line indicates the actual time to completion after accounting for parallelization; 50 files are analyzed in 45 minutes and 100 files in 89 minutes.}\label{fig:spfy_performance}
\end{center}
\end{figure}
